Revisions made to the paper \\ ``Two applications of logic programming to Coq''

### 2021-03-08 papers/types2020/revisions/cover.tex
some comments to rev's questions

\begin{itemize}
\item ``auto'' with conversion
\item ``auto'' with Hints (?)
\item other \dots
\end{itemize}

@@

\begin{verbatim}
page 5, Figure 1: the first inference rule (the decide inference
 rule) seems wrong. Indeed you are adopting Coq's syntx
 Ind[p](\Gamma_I := \Gamma_C) where p is a list of abstractions
 over so called uniform parameters.  You seem to never
 instantiate them in the rule. Moverover, the premise "(head A :
 T) \in \Gamma_I" is also suspicious. I would expect that premise
 to compute a substitution \sigma for p, to be applied to D in
 both premises (e.g. D\sigma).
\end{verbatim}

comment

\begin{verbatim}
It is mysterious why you choose to only use constructors: you
 never justify this restriction. There is also an hint that you
 can use the Hints that eauto uses, but this is not reflected in
 your code. How can it be?
\end{verbatim}
comment

@@

comment

@@

>>>>

From the implementation point of view, we have extended the kernel to
account for conversion: this allows us to do prolog search and
therefore PBT on Inductive definitions that mix deduction and
computation. We have also implemented some optimizations to the kernel
itself, as briefly mentioned in the conclusion. We have experimented
with adding Hints to the kernel via Coq-Elpi's \texttt{Accumulate DB}
and while this is doable, it is not particularly useful for the
intended application, namely PBT. What we're working on is modifying
the elaboration tactic of Sec 5, which already sees the local context,
to handle Hints and Inductive. However,  given the deadline, this
will be future work.

@@

\begin{verbatim}
page 5, Figure 1: the first inference rule (the decide inference
 rule) seems wrong. Indeed you are adopting Coq's syntx
 Ind[p](\Gamma_I := \Gamma_C) where p is a list of abstractions
 over so called uniform parameters ...
The alternative is that the parameters are explicitly quantified both in
\Gamma_i and \Gamma_C (the way the inductive type packet is represented
internally into Coq) and p becomes just a number that says how many of the
abstractions are parameters.
\end{verbatim}

We meant the latter alternative. This is now made explicit in the text.ù

\begin{verbatim}
It is mysterious why you choose to only use constructors: you
 never justify this restriction. There is also an hint that you
 can use the Hints that eauto uses, but this is not reflected in
 your code. How can it be?
\end{verbatim}
As anticipated before, it is immediate to add another ``decide'' rule
that picks up previously proven lemmas. That would be close to the
functionality of \texttt{Hint Resolve}, but does not literally uses
Coq's Hints facility. It is conceivable that we could write some glue
code to connect the two, but handling all the fairly sophistcated features of the Hint
mechanism is out of the scope of this paper.

@@

Well spotted: we had forgot the guard in the third clause of \texttt{insert}. The roof terms now reflects those evidence.

@@

% LocalWords:  FPC FPCs blackbox
